%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSimpleEntry}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\\
    \end{tabular*}\vspace{-4pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\noindent
\textbf{\LARGE Budi Santoso} \\
\small +62 XXX XXXX XXXX | \href{mailto:collinswarutumo@email.com}{collinswarutumo@email.com} | \href{https://linkedin.com/in/xxx}{\myuline{LinkedIn}} | \href{https://github.com/xxx}{\myuline{GitHub}} | \href{https://xxx.dev}{\myuline{Portfolio}}
\vspace{10pt}

\vspace{4pt}
\noindent\small{Full Stack Engineer with 5+ years building scalable web applications across fintech, e-commerce, and enterprise sectors. Proven expertise in frontend architecture, performance optimization, and leading cross-functional engineering teams. Passionate about developer experience and delivering high-impact solutions.}
\vspace{6pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Safaricom PLC}{Nairobi, Kenya}
      {Full Stack Developer | React, TypeScript, GraphQL, Node.js, Spring Boot}{Mar 2024 -- Present}
      \vspace{2pt}\\
      {\small\textit{Kenya's leading telecommunications provider.}}
      \resumeItemListStart
        \resumeItem{Automated Internet products buy journey impacting on a 60\% and reducing time used to purchase by 50\%.}
        \resumeItem{Developed Enterprise IT buy journey Architected a micro-frontend system serving 5M+ monthly users by implementing Module Federation with Webpack 5 and React.}
        \resumeItem{Decreased API response handling time by 40\% by migrating REST endpoints to GraphQL with Apollo Client.}
        \resumeItem{Improved mobile web performance score from 45 to 85 by implementing code splitting, lazy loading, and image optimization strategies.}
        \resumeItem{Established frontend testing culture achieving 70\% coverage by introducing Jest unit tests and Cypress E2E automation.}
      \resumeItemListEnd

    \resumeSubheading
      {Institut Teknologi Bandung}{Bandung, Indonesia}
      {AI Research Assistant | Python, HuggingFace, OpenAI API, LangChain}{Aug 2022 -- Feb 2024}
      \vspace{2pt}\\
      {\small\textit{AI and Machine Learning Research Lab at School of Electrical Engineering and Informatics.}}
      \resumeItemListStart
        \resumeItem{Published research paper on Indonesian NLP by fine-tuning LLaMA and GPT models for low-resource language tasks using HuggingFace Transformers.}
        \resumeItem{Built RAG-based question answering system achieving 88\% accuracy by integrating OpenAI embeddings with FAISS vector store and LangChain.}
        \resumeItem{Developed prompt engineering framework reducing hallucination rate by 40\% through chain-of-thought and few-shot learning techniques.}
        \resumeItem{Created automated evaluation pipeline for LLM outputs by implementing Python scripts with OpenAI API and HuggingFace datasets.}
      \resumeItemListEnd

    \resumeSubheading
      {Bukalapak}{Jakarta, Indonesia}
      {Software Engineer, Frontend | Next.js, React, TypeScript, Redis}{Jan 2021 -- Jul 2022}
      \vspace{2pt}\\
      {\small\textit{One of Indonesia's leading e-commerce marketplaces and digital payment platforms.}}
      \resumeItemListStart
        \resumeItem{Boosted search page load speed by 55\% by implementing server-side rendering with Next.js.}
        \resumeItem{Increased seller dashboard adoption by 30\% by leading a team of 3 engineers to rebuild the interface using React and TypeScript.}
        \resumeItem{Reduced production bugs by 60\% by championing TypeScript strict mode adoption across 12 frontend repositories.}
        \resumeItem{Automated 8 manual deployment processes by building CI/CD pipelines using GitHub Actions and Docker.}
        \resumeItem{Mentored 4 junior developers through pair programming sessions, resulting in 2 promotions within the team.}
      \resumeItemListEnd

    \resumeSubheading
      {Mekari}{Jakarta, Indonesia}
      {Frontend Developer | Vue.js, Nuxt.js, TypeScript, Storybook}{Feb 2020 -- Dec 2020}
      \vspace{2pt}\\
      {\small\textit{HR and accounting SaaS platform for SMEs.}}
      \resumeItemListStart
        \resumeItem{Accelerated feature delivery by 35\% by building a shared component library with 50+ reusable components using Vue.js and Storybook.}
        \resumeItem{Reduced customer support tickets by 25\% by redesigning the onboarding flow based on user research and analytics data.}
        \resumeItem{Improved developer onboarding time from 2 weeks to 3 days by creating comprehensive documentation and coding standards.}
        \resumeItem{Migrated legacy jQuery codebase to Vue.js, eliminating 15K lines of technical debt and improving maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {Xtremax}{Bandung, Indonesia}
      {Junior Frontend Developer | React, JavaScript, SASS, Webpack}{Jun 2019 -- Jan 2020}
      \vspace{2pt}\\
      {\small\textit{Regional digital agency specializing in web and mobile applications for government and enterprise clients.}}
      \resumeItemListStart
        \resumeItem{Delivered 6 client projects on time by developing responsive web applications using React and SASS.}
        \resumeItem{Reduced bundle size by 45\% by configuring Webpack code splitting and tree shaking for production builds.}
        \resumeItem{Improved website accessibility scores to WCAG AA compliance by implementing semantic HTML and ARIA attributes.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance}{Remote, Indonesia}
      {Web Developer | HTML, CSS, JavaScript, WordPress}{Jan 2018 -- May 2019}
      \vspace{2pt}\\
      {\small\textit{Independent freelance web development.}}
      \resumeItemListStart
        \resumeItem{Completed 12 freelance projects with 5-star ratings by delivering custom WordPress themes and landing pages.}
        \resumeItem{Generated Rp 50M+ in client revenue by building e-commerce websites with WooCommerce integration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section {Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Institut Teknologi Bandung}{2022 -- 2024}
      {M.Kom. Computer Science (3.85/4.00)}{Indonesia}
    \resumeSubheading
      {Universitas Padjadjaran}{2014 -- 2018}
      {S.Kom. Informatics (3.65/4.00)}{Indonesia}
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Frontend:} React.js, Next.js, Vue.js, Nuxt.js, TypeScript, JavaScript, HTML5, CSS3 \\
     \textbf{Styling:} Tailwind CSS, SASS, Styled Components, Material UI, Ant Design \\
     \textbf{State Management:} Redux, Zustand, React Query, Vuex \\
     \textbf{Backend:} Node.js, Express.js, Python, Go \\
     \textbf{Testing:} Jest, Cypress, Playwright, React Testing Library \\
     \textbf{DevOps:} Docker, Kubernetes, AWS, GCP, GitHub Actions, Jenkins \\
     \textbf{Databases:} PostgreSQL, MongoDB, Redis, GraphQL \\
     \textbf{Tools:} Git, Webpack, Vite, Figma, Jira \\
     \textbf{Methodologies:} Agile, Scrum, CI/CD, TDD, Code Review
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
